Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-06-11 03_Prep_data.Rmd
typos, spelling

source("R/AUDPC_for_single_obs.R") # Calculate AUDPC using final severity and first sign of disease - 7 days
source("R/same.R") # matches each element of a vector and does not return NAs
```

@@

We are narrowing the meta-analysis to only include treatments that used demethylation inhibitors, tebuconazole and propiconazole. 
Lets look at what type of statistical error was reported for the trials that used these fungicides.

```{r variance_types}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
   summarise(DMI_trts = length(Y_error_type)) %>%
   arrange(Y_error_type) %>%
   kable(caption = "Number of treatments for each trial and the error type reported") %>%
   #kable_styling(fixed_thead = T) %>% 
   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
```

>>>>

source("R/same.R") # matches each element of a vector and does not return NAs
```

@@

We are narrowing the meta-analysis to only include treatments using demethylation inhibitors, tebuconazole and propiconazole. 
Lets look at what type of statistical error was reported for the trials that used these fungicides.

```{r variance_types}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
   summarise(DMI_trts = length(Y_error_type)) %>%
   arrange(Y_error_type) %>%
   kable(caption = "Number of treatments for each trial and the error type reported") %>%
   #kable_styling(fixed_thread = T) %>% 
   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
```
